%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wenneker Assignment
% LaTeX Template
% Version 2.0 (12/1/2019)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Vel (vel@LaTeXTemplates.com)
% Frits Wenneker
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{scrartcl} % Font size

\usepackage{xcolor}
\usepackage{hyperref}


\input{structure.tex} % Include the file specifying the document structure and custom commands

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\title{	
	\normalfont\normalsize
	\textsc{Shanghai Jiao Tong University}\\
	\vspace{25pt}
	\rule{\linewidth}{0.5pt}\\ % Thin top horizontal rule
	\vspace{20pt}
	{\huge Boom Lite CPU Report}\\ % The assignment title
	\vspace{12pt}
	\rule{\linewidth}{2pt}\\ % Thick bottom horizontal rule
	\vspace{12pt}
}

\author{Ruihang Zhang \quad Yuetian Wang}

\date{\normalsize\today}

\begin{document}

\maketitle

\section{Overview}

In the past year we have implemented, as the course project of Computer Architecture, a fully out-of-order RISC-V CPU named Boom Lite\footnote{The source code is available at \url{https://github.com/RayZh-hs/chisel-boom/}}.

The CPU's architecture is inspired by the Berkeley Out-of-Order Machine (BOOM)\cite{Celio:EECS-2015-167}, though we made considerable simplifications to the original design to fit our time constraints. The final result is a CPU that that accomplishes:

\begin{enumerate}
	\item Full support for the RV32I instruction set, including \texttt{JAL}, \texttt{JALR}, and bit-masked memory access.
	\item Full support for the M extension, using Wallace tree multipliers and restoring division algorithms.
	\item Unified memory system based on DRAM, along with ICache and DCache support.
	\item Multi-hierarchy branch predictor, combining a two-bit saturating BTB and a RAS-based predictor.
	\item RAT-based OoO implementation to cut down on data movements.
	\item Partial OoO memory access as well as MMIO IO support.
\end{enumerate}

The CPU is written in Chisel, and has been synthesized to Verilog using Chisel's built-in FIRRTL compiler. The CPU achieved a clock frequency of over 517MHz on ASAP7 Demo, occupying under 15,000 um$^2$ of area.
We will detail on how we optimized the design to minimize area in the following sections.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
